---
title: "toy data"
output: flexdashboard::flex_dashboard
---

```{r}
# IMPORTANT: THESE PARAMETERS DEPEND ON THE EXPERIMENT, CHANGE THEM HERE IF CREATING A DASHBOARD.
# Otherwise see toy_data_analysis.R

working_dir <- "toy_data"
Times <- c(21,16,12,4,2,1,0.25,0)

##########################################################################################################
################################ No need to do anything else but knit this Rmd file ######################
##########################################################################################################
```

```{r}
library(flexdashboard)
library(tidyverse)
library(plotly)
# Also requires DT, markdown
```

```{r}
source("toy_data_analysis.R")
load("toy_data/script_results/necessary_data.RData")

create_dt <- function(x){
  DT::datatable(x, extensions = 'Buttons', options = list(dom = 'Blfrtip', buttons = c('copy', 'csv'), bPaginate = FALSE), rownames = FALSE, class = 'cell-border stripe', filter = 'top')
}
```

Data overview {data-orientation=rows}
=====================================     

Row
-----------------------------------------

### Proteome labelling (no normalization)
    
```{r}
ggplotly(p_no_norm)
```

### Proteome labelling (after normalization)

```{r}
ggplotly(p_all_norm)
``` 


### Median proteome synthesis and decay
```{r}
ggplotly(p_syndec_all_nls)
```

Row
-----------------------------------------

### Number of proteins present across pipeline steps

```{r}
create_dt(pip_step_prot)
```   

Data per cell compartment {data-orientation=rows}
=====================================     

Row
-----------------------------------------

### Proteome labelling (after normalization)
```{r fig.width=10, fig.height=2}
ggplotly(p_all_norm_CC)
```

Row
-----------------------------------------

### Median proteome synthesis and decay

```{r}
ggplotly(p_syndec_CC_nls)
```   

Half-life distribution {data-orientation=rows}
===================================== 

Row{.tabset .tabset-fade}
-----------------------------------------

### Half-life histogram
    
```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_hist)
```

### Half-life density

```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_dens)
```

Row{.tabset .tabset-fade}
-----------------------------------------

### Half-life summary
```{r}
create_dt(prot_median_all)
```

### Half-life summary (no Inf)
```{r}
create_dt(prot_median_all_noInf)
```

Half-life per cell compartment {data-orientation=rows}
===================================== 

Row{.tabset .tabset-fade}
-----------------------------------------

### Half-life histogram
    
```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_hist_CC)
```

### Half-life density

```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_dens_CC)
```

Row{.tabset .tabset-fade}
-----------------------------------------

### Half-life summary
```{r}
create_dt(prot_median_all_CC)
```

### Half-life summary (no Inf)
```{r}
create_dt(prot_median_all_noInf_CC)
```

Half-life comparisons {data-orientation=rows}
===================================== 

Row
-----------------------------------------

### Half-life entire cell {data-width=250}
    
```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_box) %>% layout(boxmode = "group")
```

### Half-life per cell compartment {data-width=750}

```{r fig.height=2, fig.width=6}
ggplotly(p_thalf_box_CC) %>% layout(boxmode = "group") %>% hide_legend()
```

Row
-----------------------------------------

### Half-life synthesis and decay comparison
```{r}
ggplotly(p_syn_deg_thalf)
```

Half-life correlation {data-orientation=rows}
===================================== 

Column 
----------------------------------------
### Half-life correlation (pearson)
```{r}
p_cor
```

### Half-life correlation (spearman)
```{r}
s_cor
```


Protein half-life table {data-orientation=rows}
=====================================     

Row 
-----------------------------------------

### Protein half-life is a weighted median of all peptides (unique pep wt = 10, non-U = 1)

```{r}
create_dt(All_mods_2)
```
    
Protein half-life per cell compartment table {data-orientation=rows}
=====================================     

Row 
-----------------------------------------

### Protein half-life is a median of all peptides (unique pep wt = 10, non-U = 1)

```{r}
create_dt(All_mods_2_CC)
```